Illusion Game Validation (Study 1)

### 2022-08-03 study1.Rmd
upload new stimuli

@@

## Discussion

>>>>

<!-- ```{r message=FALSE, warning=FALSE, cache=cache} -->
<!-- model <- glmmTMB::glmmTMB(Error ~ Illusion_Type * poly(ISI, 2) + (1|Participant), -->
<!--                     data=mutate(df, Illusion_Type = as.factor(Illusion_Type)), -->
<!--                     family="binomial") -->

<!-- estimate_relation(model, at = c("ISI", "Illusion_Type")) |> -->
<!--   ggplot(aes(x = ISI, y = Predicted, color="Illusion_Type")) + -->
<!--   geom_line() -->

<!-- model <- glmmTMB::glmmTMB(RT ~ Illusion_Type * poly(ISI, 2) + (1|Participant), -->
<!--                     data=mutate(df, Illusion_Type = as.factor(Illusion_Type)) |>  -->
<!--                       filter(Error == 0)) -->

<!-- estimate_relation(model, at = c("ISI", "Illusion_Type")) |> -->
<!--   ggplot(aes(x = ISI, y = Predicted, color=Illusion_Type)) + -->
<!--   geom_line() -->
<!-- ``` -->

@@

# Discussion
